A Case Study in Preserving a High Energy Physics Application

### 2014-03-13 paper.tex
add reference

Reproducibility is a cornerstone of the scientific process.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system).
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use.  This approach has
been used to some success with systems X, Y, and Z.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository, or a scalable filesystem.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson is to short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework,
which is built on top of the CMS software stack, CMSSW,
and uses packages provided by several other special interest groups within CMS.
While the CMSSW framework is installed locally,
the various packages used are checked out from CVS,
and the BEAN framework is stored in git.
This is scheduled to change,
as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
and special interest groups move their code to git.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

@@

(f) Build software enviroment using SCRAM and Python

(g) Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.

@@

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS, NFS, PanFS and HDFS.
More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

To completely verify the correctness of Solution 4, one virtual
machine sharing the same kernel version with the original machine is deployed.
Then the necessary software environment is configured on the virtual machine,
and the package is copied onto it, and the
experiment is repeated on the virtual machine.

One virtual machine from amazon EC2 is used to verify the reproducibility of the experiment. Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine. 
All the machines adopt x86\_64 hardware platform and linux OS.
Both the local VM and EC2 VM repeat the experiment with the help of the package generated on the original machine successfully.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{preservation-integration.eps}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}

>>>>

Reproducibility is a cornerstone of the scientific process ~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result ~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system) ~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems like JVM ~\cite{barthe2008preservation}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository ~\cite{cms2006cmssw}, or a scalable filesystem ~\cite{blomer2011cernvm}.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN ~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson is to short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD ~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework,
which is built on top of the CMS software stack, CMSSW ~\cite{cms2006cmssw},
and uses packages provided by several other special interest groups within CMS.
While the CMSSW framework is installed locally,
the various packages used are checked out from CVS,
and the BEAN framework is stored in git.
This is scheduled to change,
as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
and special interest groups move their code to git.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

@@

(f) Build software enviroment using SCRAM ~\cite{rabbertz2004cms} and Python

(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.

@@

Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one symbolic link file further referring to
another file named File2.
The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS ~\cite{howard1988scale}, NFS ~\cite{sandberg1985design}, PanFS ~\cite{welch2008scalable} and HDFS.
More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.

@@

To completely verify the correctness of Solution 4, one virtual
machine ~\cite{goldberg1974survey} sharing the same kernel version with the original machine is deployed.
Then the necessary software environment is configured on the virtual machine,
and the package is copied onto it, and the
experiment is repeated on the virtual machine.

One virtual machine from amazon EC2 ~\cite{amazon2010amazon} is used to verify the reproducibility of the experiment. Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine. 
All the machines adopt x86\_64 hardware platform and linux OS.
Both the local VM and EC2 VM repeat the experiment with the help of the package generated on the original machine successfully.

@@

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{preservation-integration.eps}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}
